\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
One more Final revision :-)

	Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.  We have also provided evidence that reconciliation, particularly using the MinT method, can mitigate the effect of poor bias correction.  Our intention in proposing a geometric interpretation is also to provoke research into new areas.  We now discuss three such possibilites.

	First, it should be possible to extend to the concept of coherence to non-linear constraints.  In these cases the coherent space may need to be defined by a manifold.  Although much more challenging, it is still possible define reconciled forecasts in terms of projections onto a manifold.  Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.  Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework, an issue that we investigate in a separate paper.

>>>>

	Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.  We have also provided evidence that bias correction before reconciliation, improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation. Our intention in proposing a geometric interpretation is also to provoke research into new areas.  We now discuss three such possibilities.

	First, it should be possible to extend to the concept of coherence to non-linear constraints.  In these cases the coherent space may need to be defined by a manifold.  Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold.  Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.  Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework. The latter two are issues we investigate in separate papers.
